### 2020-04-13 Proposal/aws_325ghz_proposal.tex

% Graphics
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\graphicspath{{Figures/}}

@@

%\newcommand{\FIXME}[1]{{\sffamily \bfseries #1}}
\newcommand{\FIXME}[1]{{\sffamily {\bfseries \textcolor{red}{FIXME:} #1}}}

@@

\noindent
\textbf{{\Large Arctic Weather Satellite (AWS) channels definition:\\Work plan}}  \vspace{5mm}\\
{\bf Patrick Eriksson}\\
Dept.\ of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

@@

>>>>

% Graphics
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\graphicspath{{Figures/}}
\usepackage{pdfpages}

@@

\newcommand{\FIXME}[1]{{\sffamily {\bfseries \textcolor{red}{FIXME:} #1}}}

@@

\noindent
\textbf{{\Large Activity on the definition of the AWS
high frequency\vspace{0.5ex}\\channels: Proposal}}  \vspace{5mm}\\
{\bf Patrick Eriksson}\\
Dept.\ of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

@@

\includepdf[pages={1}]{cv_pe_1page}
\includepdf[pages={1}]{CV_IKaur_1Page}
